### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@759db482cfa330994be4f0b8aaca418da6e11e4d 🚀

\hypertarget{including-observation-error-in-interaction-predictions}{%
\subsection{Including observation-error in interaction
predictions}\label{including-observation-error-in-interaction-predictions}}

@@

There is also an analytic way to represent this.

Normal approximation to binomial, as the total number of samples from
\(n_p\) particles approaches infinity, the sum of total successes across
all particles approaches a normal distribution with parameters

\[\mathcal{N}\bigg(n_p p_{ij}, \sqrt{n_p p_{ij}(1-p_{ij})}\bigg)\]

Corrected \(p_{ij}\) based on \(p_fn\) and \(p_tn\) as
\(p_{ij}^* = p_{ij}(1+p_{fp})(1-p_{fn})\)
\[\mathcal{N}\bigg(n_p p_{ij}^*, \sqrt{n_p p_{ij}^* (1-p_{ij}^*)}\bigg)\]

and then by normalizing back to \((0,1)\).

\[\mathcal{N}\bigg(p^*_{ij}, \sqrt{\frac{ p_{ij}(1-p_{ij})}{n_p}} \bigg)\]

We can then further truncate this, although in practice probability mass
outside (0,1) is exteremly loss.

Number of particles \(n_p\) as a uncertainty width. Nautral analogue to
number of observations of co-occurrence.

>>>>

\hypertarget{including-observation-error-in-interaction-predictions}{%
\subsection{Including observation error in interaction
predictions}\label{including-observation-error-in-interaction-predictions}}

@@

There is also an analytic way to represent approximate this distribution
using the normal approximation to binomial. As a reminder, as the total
number of samples \(n\) from a binomial distribution with success
probability \(p\) from approaches infinity, the sum of total successes
across all samples approaches a normal distribution with mean \(np\) and
variance \(np(1-p)\). We can use this to correct the estimate \(p_{ij}\)
based on the expected false-negative-rate \(p_{fn}\) and false-positive
rate \(p_{fp}\) to obtain the limiting distribution as the number of
resamples approaches infinity for the resampled \(p_{ij}^*\) for a given
number of particles \(n_p\). We do this by first adjusting for the rates
of observation error to get the mean resampled probability,
\(\bar{p_{ij}^*}\), as

\[\bar{p_{ij}^*} = p_{ij}(1+p_{fp})(1-p_{fn})\]

which yields the normal approximation

\[\mathcal{N}\bigg(n_p \bar{p_{ij}^*}, \sqrt{n_p \bar{p_{ij}^*} (1-\bar{p_{ij}^*})}\bigg)\]

which then can be converted back to a distribution of frequency of
successes to yield the final approximation

\begin{equation}\protect\hypertarget{eq:eq1}{}{\mathcal{N}\bigg(\bar{p^*_{ij}},
\sqrt{\frac{\bar{p_{ij}^*}(1-\bar{p_{ij}^*})}{n_p}} \bigg)}\label{eq:eq1}\end{equation}

We can then further truncate to remain on the interval \((0,1)\) (as the
output is a probability, although in practice often the probability mass
outside \((0,1)\) is exteremly low.

Why is this useful? Less computation, number of particles \(n_p\) as a
uncertainty width, nautral analogue to number of observations of
co-occurrence. More about this here.
